Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-20 cav2017/cav2017.tex
PC configuration

All benchmarks were discretized with different sample times using 
the approach described in the Appendix~\ref{sec:appendix}. 
All experiments were performed considering $x_{i}^{-}=-1$ and 
$x_{i}^{+}=1$ and the inputs $u_{k}=0, \forall k>0$.

>>>>

All benchmarks were discretized with different sample times using 
the approach described in the Appendix~\ref{sec:appendix}. 
All experiments were performed considering $x_{i}^{-}=-1$ and 
$x_{i}^{+}=1$ and the inputs $u_{k}=0, \forall k>0$.

We have also conducted the experimental evaluation on a 12-core 2.40 GHz
Intel Xeon E5-2440 with 96 GB of RAM and Linux OS. All times given are wall 
clock time in seconds as measured by the UNIX date command.

\textcolor{red}{we have to describe the timeout...}
